\documentclass[13pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\scshape}


% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
\cfoot{\scriptsize  Koech Andrew - CV }}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Koech Andrew:  CV (Curriculum Vitae)},
            pdfauthor={Koech Andrew},
            pdfkeywords={R Markdown, academic CV, template},
            colorlinks=true,
            linkcolor=blue,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

% Make AP style (kinda) dates for the updated/today field

\usepackage{datetime}
\newdateformat{apstylekinda}{%
  \shortmonthname[\THEMONTH]. \THEDAY, \THEYEAR}

\begin{document}


\centerline{\huge \bf Koech Andrew}

\vspace{2 mm}

\hrule

\vspace{2 mm}

\moveleft.5\hoffset\centerline{Masters Fellow, University of Bremen}
\moveleft.5\hoffset\centerline{Spittaler Strasse 1A · 28359 · Bremen,
Germany}
\moveleft.5\hoffset\centerline{ \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:koech@uni-bremen.de}{\nolinkurl{koech@uni-bremen.de}}} \hspace{1 mm}  \faPhone \hspace{1 mm}  +49
1 777 892
226  \hspace{1 mm}  \faGithub \hspace{1 mm} \href{http://github.com/koechandy}{\tt koechandy} \hspace{1 mm}      } 

\vspace{2 mm}

\hrule


\hypertarget{research-interests}{%
\section{\texorpdfstring{\textbf{RESEARCH
INTERESTS}}{RESEARCH INTERESTS}}\label{research-interests}}

\begin{itemize}
\tightlist
\item
  \emph{Clinical Trials, Machine Learning Modelling, Survival Analysis
  studies, Statistical Genomics in Oncology}
\end{itemize}

\hypertarget{education}{%
\section{\texorpdfstring{\textbf{EDUCATION}}{EDUCATION}}\label{education}}

\emph{University of Bremen} \hfill \emph{Bremen, Germany}

\begin{itemize}
\tightlist
\item
  \textbf{M.Sc} in Medical Biometry/Biostatistics \hfill Oct.~2022 -
  Sept.~2024
\end{itemize}

\emph{University of Potsdam} \hfill \emph{Potsdam, Germany}

\begin{itemize}
\tightlist
\item
  \textbf{M.Sc} in Bioinformatics \hfill Oct.~2020 - Not Completed
\end{itemize}

\emph{Jomo Kenyatta University of Agriculture and Technology}
\hfill \emph{Nairobi, Kenya}

\begin{itemize}
\item
  \textbf{B.Sc} in Biostatistics \hfill Sept.~2014 - Aug.~2018

  \begin{itemize}
  \tightlist
  \item
    ``Spatial Analysis of Child Mortality in Kenya''
  \end{itemize}
\end{itemize}

\emph{Terige Secondary School} \hfill \emph{Lessos, Kenya}

\begin{itemize}
\tightlist
\item
  \textbf{Kenya Certificate of Secondary Education} \hfill Jan 2010 -
  Nov.~2013
\end{itemize}

\hypertarget{employment}{%
\section{\texorpdfstring{\textbf{EMPLOYMENT}}{EMPLOYMENT}}\label{employment}}

\emph{International Cancer Institute} \hfill \emph{Eldoret, Kenya}

\textbf{Data Officer} \hfill Aug.~2019 - Nov.~2020

\begin{itemize}
\tightlist
\item
  Designed surveys to assess health issues in non-communicable diseases.
\item
  Prepared five articles for publication and presentation at local and
  international scientific conferences.
\item
  Wrote three research proposals or grant applications for submission to
  Pfizer and Novartis.
\item
  Prepared tables, graphs and listings to present clinical results.
\item
  Worked with investigators to formalize analysis plans and reporting
  specifications.
\item
  Develop statistical analysis plans and write program code to analyze
  data using SAS/R or Stata.
\item
  Prepared and submitted clinical trial documents for review of two
  Norvatis clinical trials, and responded to comments from the KEMRI
  Review Board.
\end{itemize}

\emph{AMPATH Oncology Institute} \hfill \emph{Eldoret, Kenya}

\textbf{Research Assistant} \hfill Sept.~2018 - Jul.~2019

\begin{itemize}
\tightlist
\item
  Oversaw registration of patients for cervical and breast cancer
  screening.
\item
  Conducted random checks for data completeness and accuracy.
\item
  Coded data as necessary prior to data entry using master coding lists.
\item
  Identified appropriate statistical tests for analyzing and modeling
  oncology data.
\item
  Compiled reports, charts and graphs that describe and interpret
  findings of analyses
\end{itemize}

\emph{Kenya Medical Research Institute - Center for Public Health
Research} \hfill \emph{Nairobi, Kenya}

\textbf{Intern} \hfill Jul.~2017 - Oct.~2017

\hypertarget{conference-presentations}{%
\section{\texorpdfstring{\textbf{CONFERENCE
PRESENTATIONS}}{CONFERENCE PRESENTATIONS}}\label{conference-presentations}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Koech, Andrew}, Emma Achieng, Edwin Odoyo, Dennis Munene, and
  Fredrick Chite Asirwa.
  2020.\href{https://doi.org/10.1158/1538-7755.DISP20-PO-249.}{Virtual
  Poster} ``Abstract PO-249: Implementing Community Cervical Mass
  Screenings in Low-Middle-Income Countries: A Project Implemented by
  the Blueprint for Success Program, International Cancer Institute in
  Kenya.'' Cancer Epidemiology, Biomarkers \& Prevention 29 (December):
  PO--249.
\item
  Kitur, Gloria, Emmah Achieng, Fredrick Chite Asirwa, Edwin Odoyo, and
  \textbf{Andrew Koech}.
  2020.\href{https://doi.org/10.1158/1538-7755.DISP20-PO-028.}{Virtual
  Poster} ``Abstract PO-028: Role of Community Outreach Activities in
  Cancer Prevention in Kenya.'' Cancer Epidemiology, Biomarkers \&
  Prevention 29 (December): PO--028.
\item
  Muchiri, Anthony, Gloria Kitur, Hussein Elias, \textbf{Andrew Koech},
  and Chite Asirwa.
  2020.\href{https://doi.org/10.1158/1538-7755.DISP20-PO-047.}{Virtual
  Poster} ``Abstract PO-047: The Role of Virtual Tumor Boards in
  Improving Patient Outcomes in Rural Settings of Sub-Saharan Africa.''
  Cancer Epidemiology, Biomarkers \& Prevention 29 (December): PO--047.
\item
  Sigu, Lamech, Fredrick Chite, Emma Achieng, and \textbf{Andrew Koech}.
  2020.\href{https://doi.org/10.1200/GO.20.54000}{Virtual Poster}
  ``Setting up Telemedicine: Internet of Things to Support Rural
  Oncology Clinics in a Low- and Middle- Income Country---a Pilot
  Project in Kenya.'' 6 (July):58--58.
\item
  \textbf{Andrew Koech}, Rose Njogu, Emma Achieng, Gloria Kitur, Chizi
  Kiti, Chite Asirwa.``Abstract : Setting Up Tools for Collecting
  Quality Data at The International Cancer Institute, Kenya - Learning
  from other Cancer Institutes, Registries and Cancer
  Clinics.''2020.\href{https://www.dropbox.com/s/lq0owvwya6dcjfh/1\%20CUGH\%202020\%20eBook_Abstracts_Global\%20Health\%20Education.pdf?dl=0}{Conference
  canceled}.11th Annual Consortium of Universities for Global Health
  Conference.18--20(April).
\item
  Kimani Peter, \textbf{Andrew Koech}, Nyambura Sarah.
  2018.{[}Oral{]}\emph{Spatial Analysis of Child Mortality in
  Kenya}.13th JKUAT Scientific, Technological, and Industrialization
  Conference.15--16 (November) 2018.
\end{enumerate}

\hypertarget{workshops}{%
\section{\texorpdfstring{\textbf{WORKSHOPS}}{WORKSHOPS}}\label{workshops}}

\textbf{Survival Analysis of Cancer Epidemiology. } \hfill Nairobi,
Kenya

\emph{University of Nairobi} \hfill 21 -- 22 Oct.~2019

\textbf{Advanced Biostatistical Methods: Multivariate models and Cluster
Randomized Trials. } \hfill Eldoret, Kenya

\emph{Moi University} \hfill 15 -- 18 Jul.~2019

\textbf{Bayesian Biostatistics Data Analysis: Theory and Practice. }
\hfill Nairobi, Kenya

\emph{Jomo Kenyatta University of Agriculture and Technology} \hfill 19
-- 23 Nov.~2018

\hypertarget{technical-skills}{%
\section{\texorpdfstring{\textbf{TECHNICAL
SKILLS}}{TECHNICAL SKILLS}}\label{technical-skills}}

\emph{\textbf{R for Everything}}

\begin{itemize}
\tightlist
\item
  Data pre-preparation (cleaning and wrangling) and statistical
  analysis/exploratory visualization with R Markdown.
\item
  Reproducible and replicable presentation and paper generation with R
  Markdown.
\item
  Version control using Git and Github with Rstudio.
\end{itemize}

\emph{\textbf{Other (non-R) Technical Skills}}

\begin{itemize}
\tightlist
\item
  SAS
\item
  MySQL
\item
  Linux
\item
  Windows
\end{itemize}

\hypertarget{non-technical-skills}{%
\section{\texorpdfstring{\textbf{NON-TECHNICAL
SKILLS}}{NON-TECHNICAL SKILLS}}\label{non-technical-skills}}

\emph{\textbf{Spoken Languages}}

\begin{itemize}
\tightlist
\item
  Deutsche (A2)
\item
  English (fluent)
\item
  Swahili (fluent)
\end{itemize}

\hypertarget{service}{%
\section{\texorpdfstring{\textbf{SERVICE}}{SERVICE}}\label{service}}

\emph{\textbf{Society Memberships}}

\begin{itemize}
\tightlist
\item
  International Biometric Society - Deutsche Region (IBS-DR)
\end{itemize}

\end{document}